
\section{Selected Literature}
\label{section:RelatedWork:SelectedLiterature}

% What is used in this paper?
This chapter has introduced multiple theoretical sources of information
presenting the theoretical influences for this master's thesis.

The paper by \cite{Zhao2019} serves as the inspiration for the use of the CNN-AE-LSTM model
in this thesis.
Influenced by \cite{Zhao2019} and \cite{Cerqueira2019} the ARIMA/SARIMA model, along with the local univariate LSTM model
is used as baseline models in this paper.
As we have seen from \cite{Cerqueira2019}, the use of neural network models is preferred when the amount of data is sufficient,
and we can therefore assume the use of new neural network models is preferred.

Additionaly, \cite{Montero-Manso2021}, \cite{Bandara2017}, \cite{Laptev} inspire exploration of new model structures for
LSTM and CNN-AE-LSTM models.
\cite{Montero-Manso2021} and \cite{Bandara2017} discuss improvements achieved through use of global models,
while \cite{Laptev} suggests the use of multi-feature multivariate models for improved performance.

For use with such model structures, \cite{Bandara2017} also suggests the use of groupings of data,
which in turn serve as inspiration for grouping of time series into datasets for experimentation.

These papers are some of the papers discussed, which serve as inspiration for the research conducted in this master's thesis.


% What paper gave us the SARIMA baseline?


% Zhao et al 2019 -> CNN-AE-LSTM and the baseline LSTM model


% What paper gave us global models?



% What papers gave us multivariate models?


% What papers gave us the ground for using neural networks insted of statistical models? Stat vs NN



% What paper gave us the grouping of data? Did we do any significant grouping based on a paper?




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Brukt
% -> Cerqueira2019 -> Viser til at neural network er foretrukket over statistiske modeller.
%    Bruker ARIMA som baseline. Derfor tenker vi det samme er lurt
% -> Viser til clustering av data som globale metoder
%    -> Montero-Manso2021
%    -> Bandara2017
% -> Viser til grupering av data etter domain knowledge, eller andre metoder
%    -> Bandara2017
% -> Use of multivariate models for use of multiple features
%     -> Laptev
% -> Use of local LSTM as baseline for the model
%     -> Zhao2019



% Ikke brukt
% -> Det er ingenting brukt fra "Forecasting E-commerce"
% -> 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%






% What was the baseline model (SARIMA) paper we based us on?
% We use CNN-AE-LSTM for model
% Using global models
% Using multivariate models
% Using data grouping

% Look at discussion... What papers are cited? What do we cite, and what do we use?
